%!TEX root = ts.tex

\rSec0[intro]{General}

\rSec1[intro.compliance]{Implementation compliance}

\pnum
Conformance requirements for this specification are those defined in subclause
4.1 in the C++ Standard. Similarly, all references to the C++ Standard in the
resulting document shall be taken as referring to the resulting document itself.
\begin{note}
Conformance is defined in terms of the behavior of programs.
\end{note}

\rSec1[intro.namespaces]{Namespaces and headers}

\pnum
Whenever a name \tcode{x} declared in subclause \ref{reflect} at namespace scope
is mentioned, the name \tcode{x} is assumed to be fully qualified as
\tcode{::std::experimental::reflect::v1::x}, unless otherwise specified.
The header described in this specification (see Table~\ref{tab:info.headers})
shall import the contents of \tcode{::std::experimental::reflect::v1} into
\tcode{::std::experimental::reflect} as if by:

\begin{codeblock}
namespace std::experimental::reflect {
  inline namespace v1 {}
}
\end{codeblock}

\pnum
Whenever a name \tcode{x} declared in the standard library at namespace scope is
mentioned, the name \tcode{x} is assumed to be fully qualified as
\tcode{::std::x}, unless otherwise specified.

\begin{floattable}{Reflection library headers}{tab:info.headers}
{l}
\topline
\tcode{<experimental/reflect>} \\
\end{floattable}

\rSec1[intro.ack]{Acknowledgements}

\pnum
This work is the result of a collaboration of researchers in industry and
academia.  We wish to thank the original authors of this TS, Mat\'{u}\v{s}
Chochl\'{i}k, Axel Naumann, and David Sankel. We also wish to thank people who
made valuable contributions within and outside these groups, including Ricardo
Fabiano de Andrade, Roland Bock, Chandler Carruth, Jackie Kay, Klaim-Jol
Lamotte, Jens Maurer, and many others not named here who contributed to the
discussion.
